\Large Taking uncertainty seriously  \newline \normalsize A  Bayesian approach

### 2022-03-16 presentations/presentationBoston/presentationBoston.Rmd
Small typo

---
title: '\Large Taking uncertainty seriously  \newline \normalsize A  Bayesian approach
  to  word embedding bias estimation '
author: Alicja Dobrzeniecka \& Rafal  Urbaniak \footnotesize \newline (LoPSE research
  group, University of  Gdansk, Vrij Universiteit Amsterdam)
date: "Boston, April Fools' Day"
output:
  beamer_presentation:
    theme: Rafal_beamerSly1
    keep_tex: yes
    slide_level: 2
  slidy_presentation: default
fontsize: 10pt
classoption: x11names, dvipsnames, bibspacing,natbib, table
urlcolor: blue
bibliography: ../../references/cosineReferences1.bib
csl: ../../references/apa-6th-edition.csl
link-citations: yes
---

>>>>

---
title: '\Large Taking uncertainty seriously  \newline \normalsize A  Bayesian approach
  to  word embedding bias estimation '
author: Alicja Dobrzeniecka \& Rafal  Urbaniak \footnotesize \newline (LoPSE research
  group, University of  Gdansk, Vrije Universiteit Amsterdam)
date: "Boston, April Fools' Day"
output:
  beamer_presentation:
    theme: Rafal_beamerSly1
    keep_tex: yes
    slide_level: 2
  slidy_presentation: default
fontsize: 10pt
classoption: x11names, dvipsnames, bibspacing,natbib, table
urlcolor: blue
bibliography: ../../references/cosineReferences1.bib
csl: ../../references/apa-6th-edition.csl
link-citations: yes
---
